Estimating Carrying Capacity for Chinook Parr using Quantile Random Forest Models

### 2020-02-05 analysis/paper/paper.Rmd
used the gaa metadata (previously saved) for the GAA table, to avoid needing to read it in from another repo.

<!-- Need to flesh out this table with better names, and add units as a column -->

```{r gaa-covars}
tibble(Covariate = gaa_covars) %>%
  left_join(readxl::read_excel('../../../QRFcapacity/data/raw/master_sample_pts/GAA_Metadata_20150506.xlsx') %>%
              mutate(FieldName = recode(FieldName,
                                        'ChanlType' = 'Channel_Type')) %>%
              select(Covariate = FieldName,
                     Name = DisplayName) %>%
              bind_rows(tibble(Covariate = "S2_02_11",
                               Name = "NorWeST Avg. Aug. Temp"))) %>%
  mutate(Scale = if_else(Covariate %in% c('NatPrin1', 
                                          'DistPrin1'),
                         'Watershed (HUC12)',
                         if_else(Covariate %in% c('WIDE_BF',
                                                  'Channel_Type',
                                                  'Elev_M'),
                                 'Site (300 m)',
                                 'Reach (2 km)'))) %>%
  left_join(model_svy_df$mod_full[[1]] %>%
              summary() %>%
              coefficients() %>%
              as_tibble(rownames = "Covariate") %>%
              select(1:3)) %>%
  # pander(caption = "(\\#tab:gaa-covars)Globally available attribute (GAA) habitat covariates used to extrapolate quantile regression forest (QRF) model predictions of spring/summer Chinook parr capacity to a larger scale (e.g., watershed, population), with their coefficients and standard errors.")
  kable(caption = "Globally available attribute (GAA) habitat covariates used to extrapolate quantile regression forest (QRF) model predictions of spring/summer Chinook parr capacity to a larger scale (e.g., watershed, population), with their coefficients and standard errors.",
        booktabs = T, 
        digits = 3)

>>>>

```{r gaa-covars}
gaa_meta = read_rds("../data/derived_data/gaa_metadata.rds")

tibble(Covariate = gaa_covars) %>%
  left_join(gaa_meta %>%
              select(Covariate = FieldName,
                     Name = DisplayName,
                     Units,
                     SpatialScale)) %>%
  mutate(Units = if_else(Units == "na",
                         as.character(NA),
                         Units),
         Units = if_else(grepl('\\^2', Units),
                         str_replace(Units, '\\^2', '$^2$'),
                         Units)) %>%
  left_join(model_svy_df$mod_full[[1]] %>%
              summary() %>%
              coefficients() %>%
              as_tibble(rownames = "Covariate") %>%
              select(1:3)) %>%
  # pander(caption = "(\\#tab:gaa-covars)Globally available attribute (GAA) habitat covariates used to extrapolate quantile regression forest (QRF) model predictions of spring/summer Chinook parr capacity to a larger scale (e.g., watershed, population), with their coefficients and standard errors.")
  kable(caption = "Globally available attribute (GAA) habitat covariates used to extrapolate quantile regression forest (QRF) model predictions of spring/summer Chinook parr capacity to a larger scale (e.g., watershed, population), with their coefficients and standard errors.",
        booktabs = T, 
        escape = F,
        digits = 3)
